Automated topic naming to support cross-project analysis of software maintenance activities

### 2011-01-22 msr/msr2011.tex
made subfig for unsupervised.

%\todo[inline]{since ROC is new-sounding, I wonder if a more lengthy explanation would be merited. An obvious question is why not precision/recall? -- ROC is hot right now and it combines both}
% Rebuttal: ROC is not new and it is what the machine learning community, search based software engineering and now the MSR community are using +  it has natural meaningful quality mappings.
\begin{figure}
  \centering
 \includegraphics[width=0.45\textwidth]{figures/unsupervised-bar}
 \caption{Performance, ROC values (range: 0-1), of unsupervised topic labelling for
   each NFR and per word-list. Dashed line indicates the performance of a random classifier. This graph shows how well the
   unsupervised topic labelling matched our manual annotations.}

%\todo[inline]{this is too tiny in print}
  \label{fig:maxdb-unsup-results}
\end{figure}

>>>>

%\todo[inline]{since ROC is new-sounding, I wonder if a more lengthy explanation would be merited. An obvious question is why not precision/recall? -- ROC is hot right now and it combines both}
% Rebuttal: ROC is not new and it is what the machine learning community, search based software engineering and now the MSR community are using +  it has natural meaningful quality mappings.
\begin{figure*}[]
\centering
\subfloat[ROC]{
 \includegraphics[width=0.45\textwidth]{figures/unsupervised-bar}
\label{fig:maxdb-unsup-results-roc}
}
\subfloat[F1]{
\includegraphics[width=0.45\textwidth]{figures/unsupervised-bar-f1}
\label{fig:maxdb-unsup-results-f1}
}
\caption[]{Performance of unsupervised topic labelling for each NFR per word-list. A) ROC values -- dashed line indicates the performance of a random classifier. B) F1 measure. Possible values range from 0--1.
%\todo[inline]{better discussion}% and graphical legend would be nice}
}
\label{fig:maxdb-unsup-results}
\end{figure*}

% \begin{figure}
%   \centering
%  \includegraphics[width=0.45\textwidth]{figures/unsupervised-bar}
%  \caption{Performance, ROC values (range: 0-1), of unsupervised topic labelling for
%    each NFR and per word-list. Dashed line indicates the performance of a random classifier. This graph shows how well the
%    unsupervised topic labelling matched our manual annotations.}

% %\todo[inline]{this is too tiny in print}
%   \label{fig:maxdb-unsup-results}
% \end{figure}
